Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-08 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2: Define "Access"

\begin{center}
\textbf{eigen-box condition:}\\ 
$\nec_I$ and $\pos_E$ are \emph{strong} modal rules: \\
$\omega$ must be a fresh name for the box they access \\ 
(in analogy to the eigen-variable condition for strong quantifier rules). \\
Every box must be accessed by \emph{exactly one} strong modal inference. \\
\vspace{0.5em}
\textbf{boxed assumption condition:} \\
assumptions should be discharged within the box where they are created.
\end{center}

>>>>

\begin{center}
\textbf{eigen-box condition:}\\ 
An modal inference is said to \emph{access}\\
 the box immediately above or below it. \\
$\nec_I$ and $\pos_E$ are \emph{strong} modal rules: \\
$\omega$ must be a fresh name for the box they access \\ 
(in analogy to the eigen-variable condition for strong quantifier rules). \\
Every box must be accessed by \emph{exactly one} strong modal inference. \\
\vspace{0.5em}
\textbf{boxed assumption condition:} \\
assumptions should be discharged within the box where they are created.
\end{center}
